---
title: '''#tidyteusday'' Analysis'
fontsize: 9pt
output:
  
  html_document: default
  pdf_document:
   latex_engine: xelatex
editor_options:
  
  chunk_output_type: console
---
<br>
```{r setup, include=FALSE}
knitr::opts_chunk$set(out.height = "\\textheight",  out.width = "\\textwidth",fig.width=9, fig.height=5)
#knitr::opts_chunk$set(echo = TRUE)
```
```{r include = FALSE}
library(tidyverse)
library(lubridate)
library(chron)
library(tidytext)
tidy_raw <- read_rds(url("https://github.com/rfordatascience/tidytuesday/blob/master/data/2019/2019-01-01/tidytuesday_tweets.rds?raw=true"))

tidy_processed <- tidy_raw%>%
  select(-contains("quoted"),-contains("coords"))%>% 
  separate(created_at,into = c("date","time") , " ")%>%
  mutate(date = as.Date(date),
         time = times(time))

custom_stop_words <-tribble(
  ~word,~lexicon,
  "#tidytuesday","CUSTOM",
  "16","CUSTOM",
  "36","CUSTOM"
)


stop_words2 <- stop_words%>%
  bind_rows(custom_stop_words)

tidy_text <- tidy_processed%>%
  unnest_tokens(word,text,token = "tweets")%>%
  anti_join(stop_words2,by = "word")

```

#The data was collected from github's[#Rstats & #TidyTuesday Tweets](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-01-01).

##Tidytuesday is a weekly data project in R from the R4Ds community, which contains a different dataset each week, today's data is from April-December 2018, for every tweet that had a "tidytuesday" hashtag.
<br>

###Quantitative analysis of tweets


General trend of "tidyteusday" hashtag, a sharp dip in late july might be caused to summer break, increasing to normal counts until end of year break.

&nbsp; 

```{r echo = FALSE}

tidy_processed%>%
  count(date = floor_date(date,"week"),sort = TRUE)%>%
  ggplot(aes(date,n))+
  geom_line()+
  scale_x_date(date_labels = "%b",date_breaks  ="1 month")+
  labs(x = "Date",y = "# of tweets",
       title = '"#tidyteusday" trend overtime')

```
&nbsp;

&nbsp; 

&nbsp; 

&nbsp; 

&nbsp; 

&nbsp; 

&nbsp; 

&nbsp; 

&nbsp; 

Most #tidytuesday are coming from "Twitter Web Client", which is normal since most analysis is done on Desktop and laptops.

```{r echo = FALSE}
##what day and what time most of the tweets are coming from?
tidy_processed%>%
  count(date = floor_date(date,"week"),sort = TRUE, source = fct_lump(source,3))%>%
  ggplot(aes(date,n,col = source))+
  geom_line()+
  scale_x_date(date_labels = "%b",date_breaks  ="1 month")+
  labs(x = "",y = "# of tweets", col = "Source",
       title = 'Where are the most "tidyteusday" hashtags coming from?')
```

Tidytuesday datasets are submitted on a Monday which explains the gradual increase in tweets to peak on Tuesday and decrease slowly over the weekend.


```{r echo = FALSE}
tidy_processed%>%
  count(date = wday(date,label = TRUE),sort = TRUE)%>%
  ggplot(aes(date,n))+
  geom_line(aes(group = 1))+
  geom_point()+
  labs(x = "",y = "# of tweets",
       title = 'Guess which day where the hashtag "tidyteusday" peaks?')
```
&nbsp; 

&nbsp; 

&nbsp; 

Who are the most influential people on the "tidytuesday" hashtag?

**David Robinson** looks like a clear winner, which I am assuming is attributed to his successful screen-cast of tidytuesday and broadcasting it on twitter.


```{r echo = FALSE}
##Most popular people that tweet #TidyTeusday 

tidy_most_popular <- tidy_processed%>%
  group_by(name)%>%
  summarize(AverageFavorite = mean(favorite_count),
            AverageRetweet = mean(retweet_count),
            n = n())%>%
    filter(n > 10)%>%
  arrange(desc(AverageFavorite,AverageRetweet,AverageReply))%>%
  head(9)

tidy_most_popular%>%
  gather(Average,Value, -name,-n)%>%
  ggplot(aes(reorder(name,Value),Value,fill = Average))+
  geom_col(position = "dodge")+
  coord_flip()+
  labs(y= "# of tweets",x ="",fill = "",title = "Most popular people with more than 10 tweets with the tidytuesday hashtag",subtitle =" based on average favorites and retweets")

```

A majority shows an increase in contribution at the start of the year and a decrease at the end of it, this could be contributed to end of year break, or more busy schedules for more successful influencers(A wider data range could answer this problem)

```{r echo = FALSE}
##contribution of most popular users overtime
popular <- pull(tidy_most_popular[,1])

tidy_processed%>%
  filter(name %in% popular)%>%
  group_by(name,date = floor_date(date,"month"))%>%
  summarize(AverageFavorite = mean(favorite_count),
            AverageRetweet = mean(retweet_count),
            n = n())%>%
  ggplot(aes(date,n))+
  geom_line()+
  scale_x_date(date_labels = "%b",date_breaks  ="1 month")+
  facet_wrap(~reorder(name,-AverageFavorite))+
  labs(y= "# of tweets",x ="",title = "Contribution of most influential people overtime")
```
&nbsp; 

&nbsp; 

###Text analysis of tweets
Word cloud of most frequently used words in "#tidytuesday" tweets, to no surprise #rstats,data,week and #r4ds are the most accompanied words to #tidytuesday

```{r echo = FALSE ,warning= FALSE, message= FALSE}
library(wordcloud)
word_cloud <- tidy_text %>%
  count(word,sort = TRUE)

wordcloud(word = word_cloud$word,freq = word_cloud$n, max.words = 20, colors = "blue")
```
<br>
Most popular words used along side the hashtag "tidytuesday" based on average favorite and retweets.
<br><br><br><br>
```{r echo = FALSE}
##What are the most popular words assosciated with tidyteusday


tidy_text %>%
  group_by(word)%>%
  summarize(n = n(),
            AverageFavorite = mean(favorite_count),
            AverageRetweet = mean(retweet_count))%>%
  filter(n > 50)%>%
  arrange(desc(AverageFavorite))%>%
  head(20)%>%
  gather(Average,Value, -word,-n)%>%
  ggplot(aes(reorder(word,Value),Value,fill = Average))+
  geom_col()+
  coord_flip()+
  labs(x= "",y = "# of appearence",fill = "",
       title = 'What are the most popular words associated with "tidyteusday"?')
```
&nbsp; 

&nbsp; 

&nbsp; 

Finally, we explore the flavor of the month, which topics topped the charts?

Looks like [US Voter Turnout](https://github.com/rfordatascience/tidytuesday/blob/master/data/2018/2018-10-09), took first place with 28 occurences of the word, which is the same number of posted datasets in 2018, what are the chances!


```{r echo = FALSE, warning = FALSE}
##trend of words on date
library(ggrepel)


tidy_text%>%
  mutate(date = floor_date(date,"month"))%>%
  count(word,date)%>%
  bind_tf_idf(word,date,n)%>%
  group_by(date)%>%
  top_n(2, tf_idf)%>%
  arrange(desc(tf_idf))%>%
  ggplot(aes(date,n, fill = word))+
  geom_col(position = "dodge",show.legend = FALSE)+
  geom_text_repel(aes(label = word),hjust = .4, vjust =-2)+
  scale_x_date(date_labels = "%b",date_breaks  ="1 month")+
  labs(x= "", y = "# of occurence", title = 'Flavor of the month for "tidyteusday"')
 
```


